\section{Atomic processing}

\begin{frame}
 \begin{itemize}
  \item Problem: I want to process an input file in an all-or-nothing manner.
  \item Solution: Don't do it. Atomic processing isn't batch processing! Anyway, if you really need 
  an atomic processing, use a custom \code{CompletionPolicy}.
 \end{itemize}
\end{frame}

\begin{frame}
 \frametitle{Why atomic processing is a bad idea?}
 \begin{itemize}
  \item You loose the benefits of chunk-oriented processing
  \begin{itemize}
    \item speed, small memory footprint, etc.
  \end{itemize}
  \item On a rollback, you loose everything (that's perhaps the point!)
  \item The rollback can take a long time (several hours)
  \item It all depends on the amount of data and on the processing
 \end{itemize}
\end{frame}

\begin{frame}
 \frametitle{I really need an atomic processing}
 \begin{itemize}
  \item Rollback yourself, with compensating transactions  
  \item Use a transaction rollback
  \begin{itemize}
    \item It's only a never ending chunk!
  \end{itemize}
 \end{itemize}
\end{frame}

\begin{frame}[fragile]
 \frametitle{Quick and dirty, large commit interval}
 \begin{itemize}
  \item Set the commit interval to a very large value  
  \item You should never have more items!
 \end{itemize}
\begin{xmlcode}
<chunk reader="reader" writer="writer" commit-interval="1000000"/>
\end{xmlcode}
\end{frame}

\begin{frame}[fragile]
 \frametitle{Use a never-ending \code{CompletionPolicy}}
 \begin{itemize}
  \item Spring Batch uses a \code{CompletionPolicy} to know if a chunk is complete
 \end{itemize}
\begin{javacode}
package org.springframework.batch.repeat;

public interface CompletionPolicy {

  boolean isComplete(RepeatContext context, RepeatStatus result);

  boolean isComplete(RepeatContext context);

  RepeatContext start(RepeatContext parent);

  void update(RepeatContext context);

}
\end{javacode}
\end{frame}

\begin{frame}[fragile]
 \frametitle{Plugging in the \code{CompletionPolicy}}
\begin{xmlcode}
<batch:job id="atomicProcessingJob">
  <batch:step id="atomicProcessingStep">
    <batch:tasklet>
      <batch:chunk reader="reader" writer="writer" 
                   chunk-completion-policy="atomicCompletionPolicy" />
    </batch:tasklet>
  </batch:step>
</batch:job>
\end{xmlcode}
\begin{itemize}
  \item NB: remove the \code{commit-interval} attribute when using a \code{CompletionStrategy}
 \end{itemize}
\end{frame}

\begin{frame}[fragile]
 \frametitle{Which \code{CompletionPolicy} for my atomic processing?}
\begin{xmlcode}
<bean id="atomicCompletionPolicy"
      class="o.s.b.repeat.policy.DefaultResultCompletionPolicy" />
\end{xmlcode}
\end{frame}

\begin{frame}
 \frametitle{Going further...}
 \begin{itemize}  
  \item Flow in a job
  \item \code{SkipPolicy}, \code{RetryPolicy}
 \end{itemize}
\end{frame}
